---
title: "TPL_Dashboard"
author: "Vivien Yuen"
date: " `r format(Sys.time(), '%d %B, %Y %X')`"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, 
  warning = FALSE, 
  message = FALSE
)
```

<!----
```{r input_demo, eval=FALSE}
# input <- list(
#   age_group = "0 - 5"
# )
```
---->

```{r global, include=FALSE}
library(ggplot2)
# plot theme
my_theme <- function(){
ggplot2::theme_classic() %+replace%
    theme(axis.text.x   = element_text(size = 14, 
                                 angle = 90), 
          axis.text.y   = element_text(size = 14), 
          panel.grid.major = element_line(colour = "lightgrey")
    )
}
```

```{r functions}
nice_datatable <- function(df, caption = NULL, ...) {
  df %>%
    DT::datatable(
      extensions = c("Buttons", "FixedHeader", "Scroller"),
      filter = "top",
      rownames = FALSE,
      escape = FALSE,
      caption = caption,
      options =
        list(
          dom = "Brtip",
          deferRender = FALSE,
          scrollY = 300,
          scroller = TRUE,
          scrollX = TRUE,
          fixedHeader = FALSE,
          buttons = c("copy", "csv", "excel", "pdf", "print"),
          pageLength = nrow(df),
          lengthChange = FALSE,
          ...
        )
    )
}
```

# Overview {.sidebar}

This dashboard is produced by Viv and Michael for the 2023-24 TPL Season. 
It aims to let players see a visualization of their game by game statistics and ...

```{r}

pkgload::load_all("C:/Users/tyler/Documents/R Workspace/TPL.Dashboard")

weekly_data_clean = clean_weekly_stats()
plot_game_involvement = create_plot_game_involvement(weekly_data_clean)
plot_turnovers = create_plot_turnovers(weekly_data_clean)
plot_team_contribution = create_plot_team_contribution(weekly_data_clean)

gameIdNames <- list(
        gameId = unique(weekly_data_clean$gameId),
        gameName = unique(weekly_data_clean$gameIdNames)
    )
zevList <- setNames(unique(weekly_data_clean$gameId), unique(weekly_data_clean$gameIdNames))

selectInput(inputId = "gameId", label = "Game to Analyze:",
            choices = zevList)

filtered_game_data <- reactive(
    filter(weekly_data_clean, gameId %in% input$gameId)
    )

homeTeam_df <- reactive(
    filter(filtered_game_data(), teamId == homeTeamId)
)

awayTeam_df <- reactive(
    filter(filtered_game_data(), teamId == awayTeamId)
)

```


# Week 1 {data-navmenu="Game Stats"}

## Column 1 {data-width=500}

### Home Team ID
```{r}

flexdashboard::renderValueBox({
  homeTeamValue <- homeTeam_df()
  
  shortened_value <- substr(homeTeamValue$homeTeamId[[1]], 1, 25)
  display_value <- ifelse(nchar(homeTeamValue$homeTeamId[[1]]) > 25, paste0(shortened_value, "..."), shortened_value)
  
  flexdashboard::valueBox(
    value = display_value,
    caption = "Home Team",
    icon = "fas fa-shirt",
    color = "#881C00FF"
  )
})

```

### Home Team Score
```{r}

flexdashboard::renderValueBox({
  homeTeamValue <- homeTeam_df()
  flexdashboard::valueBox(
    value = sum(homeTeam_df()$goals),
    caption = "Goals",
    icon = "far fa-futbol",
    color = "grey"
  )
})

```

### Game Involvement (Goal Contributions vs Other Touches)
```{r}

plotly::renderPlotly({
     plot_game_involvement <-
         homeTeam_df() %>%
         tidyr::pivot_longer(cols = c(goal_contributions, not_goal_contributions), names_to = "GC", values_to = "Number") %>%
         # arrange(sum(goal_contributions, not_goal_contributions), goal_contributions) %>% 
         # factor(levels = c("not_goal_contributions", "goal_contributions")) %>%
         ggplot2::ggplot(ggplot2::aes(x = reorder(name, -Number, sum),
                    y = Number,
                    fill = GC)) +
         ggplot2::geom_bar(position = "stack", stat = "identity") +
         ggplot2::scale_fill_manual(values = c("#513965FF", "#785596FF"), name = "") +
         ggplot2::labs(title = NULL, 
              y = "Touches") +
         ggplot2::theme_classic() +
         theme(title = element_blank(),
             axis.title.x = element_blank(),
             axis.title.y = element_text(size = 8),
             legend.text = element_text(size = 8),
             axis.text.x = element_text(angle = 90),
             legend.position = "none")

 plotly::ggplotly(plot_game_involvement, tooltip = c("y", "fill"))

 })

```

### Contribution to Team
```{r}

plotly::renderPlotly({
    plot_team_contribution <- 
        homeTeam_df() %>% 
        
        ggplot2::ggplot(ggplot2::aes(x = percent_of_team_touches,
                   y = percent_of_team_contributions,
                   label = name)) +
    geom_point() +
    ggplot2::labs(title = NULL,
         x = "Percent of Team Touches",
         y = "Percent of Team Goal Contributions") +
    geom_point(color = "#589E40FF", fill = "#589E40FF") +
    geom_text(ggplot2::aes(label=name), 
              size=3, 
              nudge_y = 0.005) +
    ggrepel::geom_text_repel(box.padding = 0.5, force = 5, segment.alpha = 0) +
    ggplot2::theme_classic() +
    theme(title = element_blank(),
          legend.text = element_text(size = 8),
          axis.title.x = element_text(size = 8),
          axis.title.y = element_text(size = 8)) +
    scale_x_continuous(labels = scales::percent_format(scale = 100),
                       expand = expansion(mult = c(0.05, 0.1))) +
    scale_y_continuous(labels = scales::percent_format(scale = 100),
                       expand = expansion(mult = c(0.05, 0.1)))

plotly::ggplotly(plot_team_contribution, tooltip = c("x", "y"))

})

```

### Turnovers to Touches
```{r}
plotly::renderPlotly({
    plot_turnovers <- 
        homeTeam_df() %>% 
        tidyr::pivot_longer(cols = c(turnovers, not_turnovers), names_to = "TO", values_to = "Number") %>%

        ggplot2::ggplot(ggplot2::aes(x = reorder(name, -Number, sum),
                   y = Number,
                   fill = TO)) +
    ggplot2::geom_bar(position="stack", stat = "identity") +
    ggplot2::scale_fill_manual(values = c("#C2697FFF", "#9E4058FF"), name = "") +
    ggplot2::labs(title = NULL,
         y = "Touches") +
    ggplot2::theme_classic() +
    theme(title = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_text(size = 8),
          legend.text = element_text(size = 8),
          axis.text.x = element_text(angle = 90),
          legend.position = "none")

plotly::ggplotly(plot_turnovers, tooltip = c("y", "fill"))

})
```

### Home Team
```{r home team datatable}
DT::renderDataTable({
  df1 <-
    homeTeam_df()
  
  nice_datatable(df1)
})
```

## Column 2 {data-width=500}
### Away Team ID
```{r}

flexdashboard::renderValueBox({
  awayTeamValue <- awayTeam_df()
  
  shortened_value <- substr(awayTeamValue$awayTeamId[[1]], 1, 25)
  display_value <- ifelse(nchar(awayTeamValue$awayTeamId[[1]]) > 25, paste0(shortened_value, "..."), shortened_value)
  
  flexdashboard::valueBox(
    value = display_value,
    caption = "Away Team",
    icon = "fas fa-people-group",
    color = "#172869FF"
  )
})

```

### Away Team Score
```{r}

flexdashboard::renderValueBox({
  awayTeamValue <- awayTeam_df()
  flexdashboard::valueBox(
    value = sum(awayTeam_df()$goals),
    caption = "Goals",
    icon = "far fa-futbol",
    color = "grey"
  )
})

```

### Game Involvement (Goal Contributions vs Other Touches) 
```{r}
plotly::renderPlotly({
     plot_game_involvement <-
         awayTeam_df() %>%
         tidyr::pivot_longer(cols = c(not_goal_contributions, goal_contributions), names_to = "GC", values_to = "Number") %>%
         #factor(levels = c("not_goal_contributions", "goal_contributions")) %>%
         ggplot2::ggplot(ggplot2::aes(x = reorder(name, -Number, sum),
                    y = Number,
                    fill = GC)) +
         ggplot2::geom_bar(position = "stack", stat = "identity") +
         ggplot2::scale_fill_manual(values = c("#513965FF", "#785596FF"), name = "") +
         ggplot2::labs(title = NULL,
              y = "Touches") +
         ggplot2::theme_classic() +
         theme(title = element_blank(),
             axis.title.x = element_blank(),
             axis.title.y = element_text(size = 8),
             legend.text = element_text(size = 8),
             axis.text.x = element_text(angle = 90),
             legend.position = "none")

 plotly::ggplotly(plot_game_involvement, tooltip = c("y", "fill"))

 })
```

### Contribution to Team 

```{r}

plotly::renderPlotly({
    plot_team_contribution <- 
        awayTeam_df() %>% 
        
        ggplot2::ggplot(ggplot2::aes(x = percent_of_team_touches,
                   y = percent_of_team_contributions,
                   label = name)) +
    geom_point() +
    ggplot2::labs(title = NULL,
         x = "Percent of Team Touches",
         y = "Percent of Team Goal Contributions") +
    geom_point(color = "#589E40FF", fill = "#589E40FF") +
    geom_text(ggplot2::aes(label=name), size=3, nudge_y = 0.005) +
    ggrepel::geom_text_repel(box.padding = 0.5, force = 5, segment.alpha = 0) +
    ggplot2::theme_classic() +
    theme(title = element_blank(),
          legend.text = element_text(size = 8),
          axis.title.x = element_text(size = 8),
          axis.title.y = element_text(size = 8)) +
    scale_x_continuous(labels = scales::percent_format(scale = 100),
                       expand = expansion(mult = c(0.05, 0.1))) +
    scale_y_continuous(labels = scales::percent_format(scale = 100),
                       expand = expansion(mult = c(0.05, 0.005)))

plotly::ggplotly(plot_team_contribution)

})
```

### Turnovers to Touches 
```{r}
plotly::renderPlotly({
    plot_turnovers <- 
        awayTeam_df() %>% 
        tidyr::pivot_longer(cols = c(turnovers, not_turnovers), names_to = "TO", values_to = "Number") %>%

        ggplot2::ggplot(ggplot2::aes(x = reorder(name, -Number, sum),
                   y = Number,
                   fill = TO)) +
    ggplot2::geom_bar(position="stack", stat = "identity") +
    ggplot2::scale_fill_manual(values = c("#C2697FFF", "#9E4058FF"), name = "") +
    ggplot2::labs(title = NULL,
         y = "Touches") +
    ggplot2::theme_classic() +
    theme(title = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_text(size = 8),
          legend.text = element_text(size = 8),
          axis.text.x = element_text(angle = 90),
          legend.position = "none")

plotly::ggplotly(plot_turnovers, tooltip = c("y", "fill"))

})
```

### Away Team
```{r away team datatable}
DT::renderDataTable({
  df2 <-
    awayTeam_df() 
  
  nice_datatable(df2)
})
```

# Week 2 {data-navmenu="Game Stats"}

talkjsdflksajdf

# Upcoming Matchups

# Cumulative Season Stats
