---
title: "TPL Weekly Stats Dashboard"
author: "Vivien Yuen"
date: " `r format(Sys.time(), '%d %B, %Y %X')`"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
runtime: shiny
---

```{r global, include=FALSE}
pacman::p_load(rio, here, tidyverse, flexdashboard, flextable, DT, janitor, pals, visNetwork, gtsummary, vtable, adegenet, shiny, tinytex, rmarkdown, paletteer)

source(here("Clean_01_Weekly_Stats.R"))
source(here("Create_01_Weekly_Stats_Figures.R"))

# plot theme
my_theme <- function(){
theme_classic() %+replace%
    theme(axis.text.x   = element_text(size = 14, 
                                 angle = 90), 
          axis.text.y   = element_text(size = 14), 
          panel.grid.major = element_line(colour = "lightgrey")
    )
}
```

# Overview {.sidebar}

This dashboard is produced by Viv and Michael for the 2023-24 TPL Season. 
It aims to let players view a visualization of their game by game statistics and ...

```{r}
selectInput("gameID", label = "Game to Analyze:",
            choices = weekly_data_clean$gameId, selected = '49211')

```


# Week 1 {data-navmenu="Game Stats"}

## Column 1 {data-width=500}
### Game Involvement (Goal Contributions vs Other Touches)
```{r}
# Subset data for relevant game


# Game Involvement
plot_game_involvement

```

### Contribution to Team
```{r}
plot_team_contribution
```

### Turnovers to Touches
```{r}
plot_turnovers
```

## Column 2 {data-width=500}
### Game Involvement (Goal Contributions vs Other Touches) 
```{r}
plot_game_involvement
```

### Contribution to Team 

```{r}
plot_team_contribution
```

### Turnovers to Touches 
```{r}
plot_turnovers
```


# Upcoming Matchups

# Cumulative Season Stats
