---
title: "TPL_Dashboard"
author: "Vivien Yuen"
date: " `r format(Sys.time(), '%d %B, %Y %X')`"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, 
  warning = FALSE, 
  message = FALSE
)
```

<!----
```{r input_demo, eval=FALSE}
# input <- list(
#   age_group = "0 - 5"
# )
```
---->

```{r global, include=FALSE}
pacman::p_load(rio, here, tidyverse, flexdashboard, flextable, DT, janitor, pals, visNetwork, gtsummary, vtable, adegenet, shiny, tinytex, rmarkdown, paletteer, shinyobjects)

source(here("Clean_01_Weekly_Stats.R"))
source(here("Create_01_Weekly_Stats_Figures.R"))

# plot theme
my_theme <- function(){
theme_classic() %+replace%
    theme(axis.text.x   = element_text(size = 14, 
                                 angle = 90), 
          axis.text.y   = element_text(size = 14), 
          panel.grid.major = element_line(colour = "lightgrey")
    )
}
```

```{r functions}
nice_datatable <- function(df, caption = NULL, ...) {
  df %>%
    datatable(
      extensions = c("Buttons", "FixedHeader", "Scroller"),
      filter = "top",
      rownames = FALSE,
      escape = FALSE,
      caption = caption,
      options =
        list(
          dom = "Brtip",
          deferRender = FALSE,
          scrollY = 300,
          scroller = TRUE,
          scrollX = TRUE,
          fixedHeader = FALSE,
          buttons = c("copy", "csv", "excel", "pdf", "print"),
          pageLength = nrow(df),
          lengthChange = FALSE,
          ...
        )
    )
}
```

# Overview {.sidebar}

This dashboard is produced by Viv and Michael for the 2023-24 TPL Season. 
It aims to let players view a visualization of their game by game statistics and ...

```{r}
selectInput(inputId = "gameId", label = "Game to Analyze:",
            choices = weekly_data_clean$gameId, selected = '49211')

filtered_game_data <- reactive({
  if (input$gameId != "All") {
    filter(weekly_data_clean, gameId %in% input$gameId)
  } else {
    weekly_data_clean
  }
}) 
# 
# selectInput(inputId = "homeTeam", label = "Home team:",
#             choices = filtered_game_data()$teamId)
# 
# filtered_home_team_data <- reactive({
#   if (input$homeTeam != "All") {
#     filter(filtered_game_data(), teamId %in% input$homeTeam)
#   } else {
#     filtered_game_data()
#   }
# }) 
# 
# 
# selectInput(inputId = "awayTeam", label = "Away team:",
#             choices = filtered_game_data()$teamId)
# 
# filtered_away_team_data <- reactive({
#   if (input$awayTeam != "All") {
#     filter(filtered_game_data(), teamId %in% input$awayTeam)
#   } else {
#     filtered_game_data()
#   }
# }) 
```


# Week 1 {data-navmenu="Game Stats"}

## Column 1 {data-width=500}
### Game Involvement (Goal Contributions vs Other Touches)
```{r}

plotly::renderPlotly({
     plot_game_involvement <-
         filtered_game_data() %>%
         pivot_longer(cols = c(not_goal_contributions, goal_contributions), names_to = "GC", values_to = "Number") %>%
         #factor(levels = c("not_goal_contributions", "goal_contributions")) %>%
         ggplot(aes(x = reorder(name, -Number, sum),
                    y = Number,
                    fill = GC)) +
         geom_bar(position = "stack", stat = "identity") +
         scale_fill_manual(values = c("#513965FF", "#785596FF"), name = "") +
         labs(title = NULL) +
         theme_classic() +
         theme(title = element_blank(),
             axis.title.x = element_blank(),
             axis.title.y = element_blank(),
             legend.text = element_text(size = 8),
             axis.text.x = element_text(angle = 90),
             legend.position = "none")

 plotly::ggplotly(plot_game_involvement)

 })

```

### Contribution to Team
```{r}

plotly::renderPlotly({
    plot_team_contribution <- 
        filtered_game_data() %>% 
        
        ggplot(aes(x = percent_of_team_touches,
                   y = percent_of_team_contributions,
                   label = name)) +
    geom_point() +
    labs(title = NULL,
         x = "Percent of Team Touches",
         y = "Percent of Team Goal Contributions") +
    geom_point(color = "#589E40FF", fill = "#589E40FF") +
    geom_text_repel(box.padding = 0.5, force = 5, segment.alpha = 0) +
    theme_classic() +
    theme(title = element_blank(),
          legend.text = element_text(size = 8)) +
    scale_x_continuous(labels = scales::percent_format(scale = 100),
                       expand = expansion(mult = c(0.05, 0.1))) +
    scale_y_continuous(labels = scales::percent_format(scale = 100),
                       expand = expansion(mult = c(0.05, 0.1)))

plotly::ggplotly(plot_team_contribution)

})

```

### Turnovers to Touches
```{r}
plotly::renderPlotly({
    plot_turnovers <- 
        filtered_game_data() %>% 
        pivot_longer(cols = c(turnovers, not_turnovers), names_to = "Turnovers", values_to = "Number") %>%

        ggplot(aes(x = reorder(name, -Number, sum),
                   y = Number,
                   fill = Turnovers)) +
    geom_bar(position="stack", stat = "identity") +
    scale_fill_manual(values = c("#C2697FFF", "#9E4058FF"), name = "") +
    labs(title = NULL) +
    theme_classic() +
    theme(title = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          legend.text = element_text(size = 8),
          axis.text.x = element_text(angle = 90),
          legend.position = "none")

plotly::ggplotly(plot_turnovers)

})
```

### Home Team
```{r home team datatable}
DT::renderDataTable({
  df <-
    filtered_game_data() %>% select(name:other_touches)
  
  nice_datatable(df)
})
```

## Column 2 {data-width=500}
### Game Involvement (Goal Contributions vs Other Touches) 
```{r}
plot_game_involvement
```

### Contribution to Team 

```{r}
plot_team_contribution
```

### Turnovers to Touches 
```{r}
plot_turnovers
```

### Away Team
```{r away team datatable}
DT::renderDataTable({
  df <-
    filtered_game_data() %>% select(name:other_touches)
  
  nice_datatable(df)
})
```

# Upcoming Matchups

# Cumulative Season Stats
